MS_CNuptake.Rmd

### 2022-10-18 MS_CNuptake.Rmd
make sure figs 3 and 4 are only dealing with forest

# Effect on Nup
```{r}
#work on effect of each factor on NUE
#now, work on NUE
nue_final <- all_maps$NUE # by default

@@

#SDGVM
SDGVM_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/SDGVM_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
SDGVM_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/SDGVM_S2_npp_ANN_mean.nc"), varnam = "npp"))
```

```{r warning=FALSE}
#all_maps
#not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

@@

#first, our model - using predicted data
BP_dataset3 <- na.omit(NPP_forest[,c("pred_npp","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a","lon","lat")])
BP_dataset3<- aggregate(BP_dataset3,by=list(BP_dataset3$lon,BP_dataset3$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

@@

@@

```{r, warning=FALSE}
#nue model for TRENDY
#nuptake figure
#N minerlization
NUE_test <- NPP_all

@@

#also, our simulations
NPP_grassland_remove <- NPP_grassland
forest_NUE <- NPP_forest[,c("lon","lat","pred_nuptake","pred_npp","Tg_a","PPFD_a","vpd_a")]
grassland_NUE <- NPP_grassland_remove[,c("lon","lat","grassland_pred_nuptake","grassland_pred_npp","Tg_a","PPFD_a","vpd_a")]
names(grassland_NUE) <- c("lon","lat","pred_nuptake","pred_npp","Tg_a","PPFD_a","vpd_a")
nue_allplots <- as.data.frame(rbind(forest_NUE,grassland_NUE))
nue_allplots$nue <-nue_allplots$pred_npp/nue_allplots$pred_nuptake
nue_allplots <- na.omit(nue_allplots[,c("nue","Tg_a","vpd_a","PPFD_a","lon","lat")])
nue_allplots <- aggregate(nue_allplots,by=list(nue_allplots$lon,nue_allplots$lat), FUN=mean, na.rm=TRUE)

>>>>

# Effect on Nup
```{r}
#work on effect of each factor on NUE
#now, work on NUE
nue_final <- available_grid2*npp_f/nuptake_f # by default

@@

#SDGVM
SDGVM_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/SDGVM_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
SDGVM_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/SDGVM_S2_npp_ANN_mean.nc"), varnam = "npp"))

#all_maps
#not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

```{r warning=FALSE}

@@

@@

#first, our model - using predicted data
NPP_forest2 <- subset(NPP_forest,TNPP_1>0)
BP_dataset3 <- na.omit(NPP_forest2[,c("pred_npp","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a","lon","lat")])
BP_dataset3<- aggregate(BP_dataset3,by=list(BP_dataset3$lon,BP_dataset3$lat), FUN=mean, na.rm=TRUE)%>% dplyr::select(-c(Group.1,Group.2,lon,lat,site_a))

@@

```{r, warning=FALSE}
#nue model for TRENDY
NUE_test1 <- subset(NPP_forest,TNPP_1>0)
NUE_test2 <- subset(NPP_forest,is.na(Nmin)==FALSE)
NUE_test <- rbind(NUE_test1,NUE_test2)

@@

#also, our simulations
NUE_test1 <- subset(NPP_forest,TNPP_1>0)
NUE_test2 <- subset(NPP_forest,is.na(Nmin)==FALSE)
NUE_test <- as.data.frame(rbind(NUE_test1,NUE_test2))
nue_allplots <- NUE_test[,c("lon","lat","pred_nuptake","pred_npp","Tg_a","PPFD_a","vpd_a")]

nue_allplots$nue <-nue_allplots$pred_npp/nue_allplots$pred_nuptake
nue_allplots <- na.omit(nue_allplots[,c("nue","Tg_a","vpd_a","PPFD_a","lon","lat")])
nue_allplots <- aggregate(nue_allplots,by=list(nue_allplots$lon,nue_allplots$lat), FUN=mean, na.rm=TRUE)
